Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-26 index.qmd
add updates

  total <- validation %>% 
  dtplyr::lazy_dt() %>% 
  group_by(res,true) %>% 
  dplyr::summarise(agreed = sum(same, na.rm = T),
          n_obs = n()) %>% 
  # ungroup() %>% 
  mutate(prop = agreed/n_obs) %>% 
  as_tibble() %>% 
  dplyr::filter(true != 1,
                true != 6,
                true != 7,
                true != 8) %>% 
  mutate(true_fct = as.factor(true),
         area = res*res)

@@

# glm_res_true <- glm(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit")) 
glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))

@@

NewData<-expand_grid(res=unique(total$res),
                    true_fct=unique(total$true_fct),
                    area = res*res)

@@

NewData <- NewData %>% 
  mutate(fit = pred$fit*100,
         se = pred$se.fit*100,
         true_fct=as.factor(true_fct))

@@

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area)/100, y = fit,
                color = true_fct, group = true_fct
                ))+
  # ylim(0,1)+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm"))

>>>>

  total <- validation %>% 
  dtplyr::lazy_dt() %>% 
  group_by(res,true) %>% 
  dplyr::summarise(agreed = sum(same, na.rm = T),
          n_obs = n()) %>% 
  # ungroup() %>% 
  mutate(prop = agreed/n_obs) %>% 
  as_tibble() %>% 
  # dplyr::filter(true != 1,
  #               true != 6,
  #               true != 7,
  #               true != 8) %>% 
  mutate(true_fct = as.factor(true),
         area = res*res)

@@

glm_res_true <- glm(prop ~ area*true_fct , data = total)
# glm_res_true <- mgcv::gam(prop ~ area * true_fct , data = total, familly = mgcv::betar(link="logit"))

a <- total %>% 
  group_by(res, true) %>% 
  reframe(mean = mean(prop))

@@

NewData<-expand_grid(area=unique(total$area),
                    true_fct=unique(total$true_fct))

@@

NewData <- NewData %>% 
  mutate(fit = pred$fit*100,
         se = pred$se.fit*100,
         true_fct=(true_fct))

@@

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area), y = fit,
                color = true_fct, group = true_fct
                ))+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm")
          )
